Envelope Estimation using Geometric Properties of a Discrete Real Signal

### 2020-12-06 Papers/01_Pulses_Envelope/PulsesEnvelope.tex
last adjustments

% \usepackage{hyperref}
% \usepackage{hypcap}
% \hypersetup{
%   colorlinks=true, 
%   allcolors=black,
%   pdfauthor={Carlos Henrique Tarjano Santos},
%   pdftitle={Robust Digital Envelope Estimation Via Geometric Properties of an Arbitrary Real Signal}
% }

@@

{\bf Keywords:} DSP, alpha shapes, envelope detection, discrete curvature estimation, demodulation

@@

\section{Methodology}
After defining what will be considered an envelope in the context of this work, in this section we explore some simplifications that can be applied to a discrete wave, defining the representation that will be used in the subsequent part of the work.

@@

\begin{align} \label{eq:Envelope}
  & \textbf{w}, \textbf{e}, \textbf{c} \in \mathbb{R}^n \\
  & \textbf{w} = (w_0, w_1, \cdots, w_{n-1}) \\
  & \textbf{e} = (e_0, e_1, \cdots, e_{n-1}) \\
  & \textbf{c} = (c_0, c_1, \cdots, c_{n-1}) \\
  & \textbf{w} = \textbf{e} \odot \textbf{c} \quad \therefore \quad w_i = e_i c_i \quad \forall \quad i, 0 \le i \le n-1
\end{align}

@@

\section{Results}
Given the lack of a precise definition of what an envelope should be, we begin this section suggesting an empirical metric, based on the behaviour of the carrier wave \textbf{c}. We also comment on some metrics presented in the literature, and compare our algorithm with traditional demodulation approaches, both in relation to execution time and accuracy; to this last end, a numerical indicator is also introduced.

@@

\section{Approximated location of pseudo-cycles}

@@

The present work also highlights some gaps in our current understanding and definition of temporal envelope and, in so doing, endeavors to motivate further research in this topic, that can ultimately give rise to a more mathematically sound envelope theory, especially concerning broadband waves; suggestions in this direction are also presented.

>>>>

\usepackage{hyperref}
\usepackage{hypcap}
\hypersetup{
  colorlinks=true, 
  allcolors=black,
  pdfauthor={Carlos Henrique Tarjano Santos},
  pdftitle={Robust Digital Envelope Estimation Via Geometric Properties of an Arbitrary Real Signal}
}

@@

{\bf Keywords:} DSP; alpha shapes; envelope detection; discrete curvature estimation; demodulation

@@

\section{Methods}
After defining what will be considered an envelope in the context of this work, in this section we explore some simplifications that can be applied to a discrete wave, defining the representation that will be used in the subsequent part of the work.

@@

\begin{align} \label{eq:Envelope}
  & \mathbf{w}, \mathbf{e}, \mathbf{c} \in \mathbb{R}^n \\
  & \mathbf{w} = (w_0, w_1, \cdots, w_{n-1}) \\
  & \mathbf{e} = (e_0, e_1, \cdots, e_{n-1}) \\
  & \mathbf{c} = (c_0, c_1, \cdots, c_{n-1}) \\
  & \mathbf{w} = \mathbf{e} \odot \mathbf{c} \ \therefore \ w_i = e_i c_i \ \forall \ i, \ 0 \le i \le n-1
\end{align}

@@

\section{Results and Discussion}
Given the lack of a precise definition of what an envelope should be, we begin this section suggesting an empirical metric, based on the behaviour of the carrier wave \textbf{c}. We also comment on some metrics presented in the literature, and compare our algorithm with traditional demodulation approaches, both in relation to execution time and accuracy; to this last end, a numerical indicator is also introduced.

@@

\subsection{Approximated location of pseudo-cycles}

@@

The present work also highlights some gaps in our current understanding and definition of temporal envelope and, in so doing, endeavours to motivate further research in this topic, that can ultimately give rise to a more mathematically sound envelope theory, especially concerning broadband waves; suggestions in this direction are also presented.
